%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Credit Analyst} % Job title
    {Volkswagen Finance.} % Organization
    {} % Location
    {Jan. 2013 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed financial data (budgets and income) with consideration for the company's goals.}
        \item {Improved existing and created new products to push the company's finance results}
        \item {Completed dealer's financial analysis and converted data into actionable insights.}
        \item {Used SQL \& Advanced Excel to track and analyze sales, industry rankings and payment records data.}
        \item {Developed key risk indicators to monitor financial risks and decreased costs by 8\%.}
        \item {Utilized Tableau, and SSRS dashboard/visualization tools for data intelligence and analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Investment Accounting} % Job title
    {Heng An Standard Life Insurance Co.} % Organization
    {} % Location
    {Sep. 2011 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Synthesized and analyzed process bonds, funds, assisted in analysis of investment products.}
        \item {Responsible for investment valuation, calculated investment price and assets.}
        \item {Generated reports, charts, and tables on cash flow statement, balance sheet, income statement.}
        \item {Tracked actual financial results, compared and corrected data in regards to transactions.}
        \item {Recommend, developed rules and projects that improving team competitive position.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Account Manager} % Job title
    {Shenzhen Development Bank.} % Organization
    {} % Location
    {Jul. 2008 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Audited client financial needs, wrote investigation reports, complete credit rating.}
        \item {Collected and provided necessary info for credit decisions, solved problems found in vetting.}
        \item {Communicated and coordinated project discussions and inspected the assessment for credit risk.}
        \item {Responsible for loan management work, regular loans, tracked usage per customer.}
        \item {Managed 3 big projects that had over 30 enterprise customer loans.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
