%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Applied Data Analytics: Part-time, Certificate} % Degree
    {BCIT(British Columbia Institute of Technology)} % Institution
    {Vancouver, BC} % Location
    {Jun. 2016 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {COMP 1630 - Relational Database Design and SQL.}
        \item {COMP 2256 - Visual Analytics for Business Intelligence with Tableau.}
        \item {COMP 2362 - Microsoft Excel Advanced (Grade: A 93).}
        \item {COMP 2831 - Business Analysis and Systems Design.}
        \item {COMP 3838 - Data Warehouse Foundations for Business Intelligence (Grade: A 92).}
        \item {MATH 1060 - Statistics for Data Analysis.}
        \item {MATH 3060 - Advanced Statistical Techniques for Data Analytics (Grade: A+ 96).}
        \item {COMP 3839 - Data Quality Improvement (Grade: A 92).}
        \item {COMP 3704 - Applied IT Security Fundamentals.}
        \item {COMP 2854 - Data Analytics Fundamentals (Grade: A+ 96).}
        \item {COMP 4679 - Business Intelligence with SSRS, SQL Server Reporting Services (Grade: A 93).}
        \item {COMP 4254 - Advanced Topics in Data Analytics (Grade: A 91).}
        \item {COMP 3840 - Introduction to Big Data and Hadoop.}
        \item {COMP 1288 - IT Project Management (Grade: A+ 95).}
        \item {COMP 4681 - Business Intelligence with SSAS, SQL Server Analysis Services (Grade: A+ 97).}
        \item {BLAW 3205 - Internet and IT Law.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {B.S. in Finance} % Degree
    {NKU(Nankai University)} % Institution
    {Tianjin, China} % Location
    {Sep. 2004 - Jul. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
